---
title: "Stats 101A Project"
author: "Group 11"
date: "2023-02-28"
output:
  pdf_document: default
  html_document: default
---

Lecture 1, Section 1B, Group 11: Shiyu Murashima, Andrew Chen, Connie Ma, Daniel Kao, Rebekah Limb, Zoey Meng

## Loading in Data
```{r}
# change to your file directory
data <- read.csv("/Users/ShiyuMurashima/Downloads/archive/Admission_Predict_Ver1.1.csv")
data <- data[,c(-1)] # removed Serial Number column
attach(data)
```

## Correlation Matrix
```{r}
cor(data)
pairs(data)
```

## Summary Statistics
```{r}
summary(data)

# standard deviations
sd(GRE.Score)
sd(TOEFL.Score)
sd(University.Rating)
sd(SOP)
sd(LOR)
sd(CGPA)
sd(Research)
sd(Chance.of.Admit)
```

## Full Model
```{r}
m1 <- lm(Chance.of.Admit ~ GRE.Score + TOEFL.Score + University.Rating + SOP + 
           LOR + CGPA + Research)
summary(m1)
anova(m1)
```

```{r}
par(mfrow = c(2, 2))
plot(m1)
```

## Box-Cox Power Transformation
```{r}
library(car)
# removed Research categorical column (0 returns -inf)
summary(powerTransform(cbind(GRE.Score, TOEFL.Score, University.Rating, SOP, LOR,
                             CGPA, Chance.of.Admit) ~ 1))
```

## Inverse Response Plot
```{r}
#inverse response plot
invResPlot(m1)
```

## Y Transformed
```{r}
m2 <- lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + University.Rating + SOP + 
           LOR + CGPA + Research)
summary(m2)

par(mfrow = c(2, 2))
plot(m2)
```

## X and Y Transformed
```{r}
t1 <- GRE.Score^5.2354 
t2 <- TOEFL.Score^2.2176
t3 <- University.Rating^0.9145
t4 <- SOP^1.3312
t5 <- LOR^1.2129
t6 <- CGPA^3.2932
t7 <- Research

m3 <- lm(data[,8]^2.5597 ~ t1 + t2 + t3 + t4 + t5 + t6 + t7)
summary(m3)

par(mfrow = c(2, 2))
plot(m3)
```

## Checking Validity (omit)
```{r}
# stanres1 <- rstandard(m2)
# par(mfrow = c(2, 3))
# plot(log(GRE.Score), stanres1)
# plot(log(TOEFL.Score), stanres1)
# plot(log(University.Rating), stanres1)
# plot(log(SOP), stanres1)
# plot(log(LOR), stanres1)
# plot(log(CGPA), stanres1)
# plot(log(Research), stanres1)
```

## AV Plots and VIF
```{r}
par(mfrow = c(2, 4))
avPlot(m2, variable = GRE.Score, ask = FALSE)
avPlot(m2, variable = TOEFL.Score, ask = FALSE)
avPlot(m2, variable = University.Rating, ask = FALSE)
avPlot(m2, variable = SOP, ask = FALSE)
avPlot(m2, variable = LOR, ask = FALSE)
avPlot(m2, variable = CGPA, ask = FALSE)
avPlot(m2, variable = Research, ask = FALSE)

vif(m2)
```

## Method of All Subsets: R^2adj and BIC
```{r}
library(leaps)

X <- cbind(GRE.Score, TOEFL.Score, University.Rating, SOP, LOR, CGPA, Research)
b <- regsubsets(as.matrix(X), data[, 8]^2.654852)
c <- summary(b)

cbind(c$which, round(cbind(adjr2=c$adjr2, bic=c$bic), 3))

# Radj2: Best with SOP or none removed
# BIC: Best with SOP removed
```

## Method of All Subsets: AIC
```{r}
extractAIC(m2)[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + University.Rating + 
                LOR + CGPA + Research))[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + LOR + CGPA + 
                Research))[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ TOEFL.Score + University.Rating + CGPA + 
                Research))[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + University.Rating + CGPA))[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + CGPA))[2]
extractAIC(lm(Chance.of.Admit^2.654852 ~ CGPA))[2]
# Best with SOP removed
```

## Method of All Subsets: AICc
```{r}
extractAIC(m2)[2] + 2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + University.Rating + 
                LOR + CGPA + Research))[2] + 2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + LOR + CGPA + 
                Research))[2] + 2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ TOEFL.Score + University.Rating + CGPA + 
                Research))[2] + 2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + University.Rating + CGPA))[2] + 
  2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ GRE.Score + CGPA))[2] + 
  2*(7+2) * (7+3) / (nrow(data)-7-1)
extractAIC(lm(Chance.of.Admit^2.654852 ~ CGPA))[2] + 2*(7+2) * (7+3) / (nrow(data)-7-1)
# Best with SOP removed
```

## Forward Stepwise: AIC
```{r}
forwardAIC <- step(lm(Chance.of.Admit^2.654852 ~ 1), 
                   scope = list(lower = ~ 1,
                                upper = ~ GRE.Score + TOEFL.Score + University.Rating + 
                                  SOP + LOR + CGPA + Research),
                   direction = "forward")
# Best with SOP removed
```

## Backward Stepwise: AIC
```{r}
backAIC <- step(m2, direction = "backward")
# Best with SOP removed
```

## Reduced Model (SOP Removed)
```{r}
m4 <- lm(Chance.of.Admit^2.654852 ~ GRE.Score + TOEFL.Score + University.Rating + 
           LOR + CGPA + Research)
anova(m4, m2)
```

## Final Model
```{r}
summary(m4)
anova(m4)
```

```{r}
par(mfrow = c(2, 2))
plot(m4)
```
